The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-16 analysis/paper/paper.qmd
Specify the language of the corpus

The theses are available in PDF format with complex layouts typical to an urbanism project in which text and various types of graphics are combined.

@@

Word-level tokenisation was applied with the `unnest_tokens()` function of the `tidytext` package. This was preferred over other tokenisers as it produced results that work seamlessly with other `tidyverse` tools.

@@

```{r}
# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_theses_words, 
                           top_n = 3, 
                           title_col = "title", 
                           word_col = "word")
```

```{r}
# Which are the top n most frequently used words in all theses`?
get_top_words_per_corpus(data = emu_theses_words, 
                         top_n = 5, 
                         word_col = "word")
```

```{r}
# Which theses contain "fabric" in the top 20 most frequently used words?
emu_theses_top_20 %>% 
  filter(word == "fabric")

>>>>

The theses are available in PDF format with complex layouts typical to an urbanism project in which text and various types of graphics are combined. With the exception of a bilingual English-Spanish thesis, all thesis were written in English.

@@

Word-level tokenisation was applied with the `unnest_tokens()` function of the `tidytext` package. This was preferred over other tokenisers as it produced results that work seamlessly with other `tidyverse` tools used in the analysis.

@@

```{r}
# Which are the top 20 most frequently used words in each thesis?
emu_theses_top_20 <- emu_theses_words %>%
  group_by(title) %>%
  count(word, sort = TRUE) %>%
  slice_max(n, n = 20) %>%        ### top_n is superseded; better use slice_max instead
  # filter(n > 50) %>%              ### filter words with a minimum count
  ungroup() %>% 
  mutate(word = reorder(word, n))

# Which are first 5 most frequently used words in each thesis?
emu_theses_first_5 <- emu_theses_words %>%
  count(title, word) %>% 
  group_by(title) %>% 
  arrange(desc(n)) %>% 
  slice(1:5)

# Which theses contain "fabric" in the top 20 most frequently used words?
emu_theses_top_20 %>% 
  filter(word == "fabric")
